A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-12-10 article/02_Materials_and_Methods.Rmd
added figure preliminary
better place and way to embed the plot matrix

The continuous time series of year wise burial rite proportions for each region allow to calculate time series of a measure of cultural distance for each region-region relation (Figure **TODO**). Several different measures of cultural distance could be used here following the discussion of these matters in the relevant literature (**citation**). In this context the Squared Euclidian Distance (SED) seems to be a sensible statistic, because it is fairly simple, works with only few assumptions and emphasizes differences through squaring.

>>>>

The continuous time series of year wise burial rite proportions for each region allow to calculate time series of a measure of cultural distance for each region-region relation (Figure \ref{sed_region_matrix}). Several different measures of cultural distance could be used here following the discussion of these matters in the relevant literature (**citation**). In this context the Squared Euclidian Distance (SED) seems to be a sensible statistic, because it is fairly simple, works with only few assumptions and emphasizes differences through squaring.

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{../analysis/figures/sed_region_matrix.jpeg}
\caption{\label{sed_region_matrix}This is a figure.}
\end{figure*}
